moderated_regressions

### 2024-04-28 moderated_regressions.Rmd
example table

---
title: "moderated_regressions"
output: html_document
date: "2024-04-13"
---

@@

```{r Numbers for Tables}
summary(challenge_resource_burnout_model3)$coefficients

#estimates - b weights
summary(challenge_resource_burnout_model3)$coefficients[1, 1]
summary(challenge_resource_burnout_model3)$coefficients[1, 2]
summary(challenge_resource_burnout_model3)$coefficients[1, 3]
summary(challenge_resource_burnout_model3)$coefficients[1, 4]

# p values
summary(challenge_resource_burnout_model3)$coefficients[4, 1]
summary(challenge_resource_burnout_model3)$coefficients[4, 2]
summary(challenge_resource_burnout_model3)$coefficients[4, 3]
summary(challenge_resource_burnout_model3)$coefficients[4, 4]

#F values (these are just the change from model 2 with main effects to model 3 that adds the interaction)
challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
challenge_resource_burnout_anova$F
challenge_resource_burnout_anova$`Pr(>F)`

#r squared
summary(challenge_resource_burnout_model2)
summary(challenge_resource_burnout_model2)$coefficients[3, 1]

summary(challenge_resource_burnout_model3)
```

>>>>

---
title: "moderated_regressions"
output: pdf_document
date: "2024-04-13"
---

@@

```{r Numbers for Tables}

options(scipen=999)  ## Suppresses scientific notation

# b weights
chal.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[2, 1],6)
res.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[3, 1],6)

int.3.burn <- round(summary(challenge_resource_burnout_model3)$coefficients[4, 1],6)

#r squared
challenge_resource_burnout_model2_r <- round(summary(challenge_resource_burnout_model2)$r.squared,4)
challenge_resource_burnout_model3_r <- round(summary(challenge_resource_burnout_model3)$r.squared,4)

## R square change
challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
challenge_resource_burnout_r_square_change <- round(challenge_resource_burnout_model3_r - challenge_resource_burnout_model2_r,4)

```{r, results='asis'}

library(kableExtra)

DV <- c("Burnout","","")
Step <- c("1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource")
b <- c(chal.2.burn,res.2.burn,int.3.burn)
DeltaR <- c("",paste(challenge_resource_burnout_model2_r,"**"),challenge_resource_burnout_r_square_change)

regtable <- cbind(DV, Step, Model, b, DeltaR)

papaja::apa_table(regtable)
